### 2017-10-05 Sections/economics_of_the_quantum_internet.tex
Added repeater network figures
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks

\subsubsection{Combined computational scaling functions}\index{Combined computational scaling functions}

@@

Consider taking a single unit of time (i.e we are ignoring cost discounting over multiple units of time) and dividing it amongst a number of nodes, $n_\text{nodes}$, each with their own scaling function, $f_\text{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\text{sc}^\text{(joint)}$, of a group of participants, each with their own scaling functions, $f_\text{sc}^{(i)}$, is given by,
\begin{align}
	t_\text{joint} &= \sum_{i=1}^{n_{\text{nodes}}} \beta_i \cdot f_\text{sc}^{(i)}(n_\text{global}) \nonumber \\
	&= f_\text{sc}^\text{(joint)}(n_\text{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\text{nodes}} \beta_i = 1.
\end{align}

@@

Thus, the joint scaling function of the entire network is simply given by a linear combination of the scaling functions of the different market participants.

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=\columnwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.\comment{Colours are fucked.}} \label{fig:NPSF}
\end{figure}

@@

Some of these assumptions may reasonably turn out to be invalid, or require revision as we learn more about upcoming quantum technologies and the trajectories their marketplace will follow. However, for ease of exposition, and the purposes of presenting some initial rudimentary, qualitative analyses and thought experiments, these assumptions simplify our derivations and act as a good starting point for future work.

@@

In Secs.~\ref{sec:quant_ec_lev} \& \ref{sec:GVQC} we argue that because of the super-linear scaling in the computational power of networked quantum computers, it will be most economically efficient to unify the world's entire collective quantum computational resources over the network and time-share their joint computational power. For this reason, we will assume that global quantum computing resources are unified, and time-shared equitably (as described in Sec.~\ref{sec:arb_free_time_share}), overseen by a trusted central authority, compliant with our efficient market assumptions (Sec.~\ref{sec:eff_markets}).

However, as discussed in Sec.~\ref{sec:GVQC}, it may be the case that competing strategic interests will drive a wedge between the quantum resources of competitors and adversaries, partitioning them into a set of smaller networks, divided across strategic boundaries. In this instance, the arguments presented in the upcoming sections will apply to these smaller networks individually.

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on an exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point of this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N_t = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

The exact value of the growth rate, $\gamma_N$, is obviously unclear at such early stages. Although in the the case of classical computing we have seen a very consistent doubling of computational power roughly every 18 months. This may very well be different for quantum technologies, owing to their fundamentally different engineering requirements.

@@

Let the dollar cost of physical qubits follow Moore's Law-like dynamics, decreasing exponentially with time,
\begin{postulate}[Hardware cost]\label{post:hardware_cost}\index{Hardware cost}
The dollar-cost of a single physical qubit scales inverse exponentially as,
\begin{align}
	C_t = C_0 {\gamma_C}^{-t},
\end{align}
where \mbox{$\gamma_C>1$} characterises the decay rate.
\end{postulate}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment, with $Q\to 1$ driven ever closer to unity as market competition increases, thereby closing the gap between investment and reward,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth}) and employing a combined computational scaling function (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is the product of the hardware cost per qubit and the number of qubits,
\begin{align}
	n_\text{invest}(t) &= N_t C_t \nonumber \\
	&= N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the cost of computation postulate,

\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation, measured in FLOPs per qubit, decreases over time as,
\begin{align}\index{Cost of computation}
	L_t \gtrapprox \frac{C_0 {\gamma_C}^{-t}}{f_\text{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}

This implies,
\begin{postulate}[Spot price of computation] The present-day (\mbox{$t=0$}) spot price of a computation is,
\begin{align}
L_0 \gtrapprox \frac{C_0}{f_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the initial value of computations simply approximates the initial hardware investment, scaled by its initial computational power, as is intuitively expected.

Note that if $f_\text{sc}$ scales linearly, as per classical computation, we observe a regular exponential decay in the cost of computation, consistent with the classical Moore's Law. On the opposing extreme, for quantum-enhanced exponential $f_\text{sc}$, the cost of computation decreases super-exponentially with time, an economic behaviour unique to post-classical computation with no classical analogue.

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-shares}\comment{Check index for doubling up}, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.

@@

\begin{definition}[Single-qubit QCL]
The single-qubit QCL is the leverage associated with adding a single qubit to the network, \mbox{$n=1$}, defined as,
\begin{align}
	\lambda_\text{qubit} = \frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}.
\end{align}
\end{definition}

@@

Forward contracts are immensely useful in conventional markets, as a means by which to secure future use or ownership of an asset at predictable points in time. For example, farmers make heavy use of forward contracts to lock in sale of their produce before it has been harvested, such that the value is locked in in advance and the sale guaranteed, providing a very valuable hedging instrument for managing risk.

@@

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{tax_exp} \\
\includegraphics[width=\columnwidth]{tax_subsidy}
\caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\text{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}	
\end{figure}

@@

%
% Subjective vs Objective Value of Computation
%

\subsubsection{Subjective vs objective value of computation}

\comment{To do}
\comment{Different users might have different scaling functions. How to reconcile into single marketplace?}

\comment{The dollar cost of a qubit at a given point in time is not affected by its application -- it's a unit of hardware. So the dollar cost per unit of hardware (manufacturing) is independent of use, but the value to the end-user varies enormously depending on their application. How do these discrepancies affect market dynamics? Does this imply that users of `slow' quantum algorithms (e.g quadratically enhanced algorithms) will be forced to pay more for a unit of computation than users employing `fast' algorithms (e.g ones with exponential computational enhancement)? This creates a `subjective cost' that is application-dependent, as opposed to the `objective cost' of the physical hardware. subjective (software) vs objective (hardware) costs. How do different parties price things differently given subjective costs vary between users?}

@@

\subsubsection{The quantum stockmarket}

\comment{To do. People don't own qubits, so the owners of qubits float their allocated time-shares on the marketplace}.

\comment{Quantum stockmarket: If all the world's QCs are networked into a single virtual QC, there needs to be a central authority overseeing the united quantum resources and allocating compute time using some kind of market mechanism. How would we construct a marketplace for this kind of trading in compute time? What kinds of dynamics would we anticipate? There will be different market forces at play by different market participants. e.g the value of a unit of QC time-share will be driven up by those running algorithms with the most profitable applications, conversely for quantum algorithms with relatively little computational enhancement. e.g quantum simulation applications run by a drug design or genetics company may have extremely high yield, whereas some obscure, niche optimisation problem may not be worth much in dollars. But all of these different users are competing on the marketplace for access to the same resources. Market cap as function of varying demand for computation.}

\comment{If different users have different scaling functions, how does this affect the relative amount they are willing to pay for time shares? Stockmarket?}

>>>>

\subsubsection{Combined computational scaling functions}\index{Combined computational scaling functions}\label{sec:comb_comp_sc_func}

@@

Consider taking a single unit of time (i.e we are ignoring cost discounting\index{Cost discounting} over multiple units of time) and dividing it amongst a number of nodes, $n_\text{nodes}$, each with their own scaling function, $f_\text{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\text{sc}^\text{(joint)}$, of a group of participants, each with their own scaling functions, $f_\text{sc}^{(i)}$, is given by,
\begin{align}
	t_\text{joint} &= \sum_{i=1}^{n_{\text{nodes}}} \beta_i \cdot f_\text{sc}^{(i)}(n_\text{global}) \nonumber \\
	&= f_\text{sc}^\text{(joint)}(n_\text{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\text{nodes}} \beta_i = 1.
\end{align}

@@

Thus, the joint scaling function of the entire network is simply given by a linear combination (weighted average) of the scaling functions of the different market participants.

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=0.47\textwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.\comment{Colours are fucked.}} \label{fig:NPSF}
\end{figure}

@@

Some of these assumptions may reasonably turn out to be invalid, or require revision as we learn more about upcoming quantum technologies and the trajectories their marketplace will follow. However, for ease of exposition, and the purposes of presenting some initial rudimentary, \textit{qualitative} analyses and thought experiments, these assumptions simplify our derivations and act as a good starting point for future, more rigorous treatment.

@@

In Secs.~\ref{sec:quant_ec_lev} \& \ref{sec:GVQC} we argue that because of the super-linear scaling in the computational power of networked quantum computers, it will be most economically efficient to unify the world's entire collective quantum computational resources over the network and time-share their joint computational power. For this reason, we will assume that global quantum computing resources are unified, and time-shared equitably (as described in Sec.~\ref{sec:arb_free_time_share}), overseen by a trusted central authority, congruent with our efficient market assumptions (Sec.~\ref{sec:eff_markets}).

However, as discussed in Sec.~\ref{sec:GVQC}, it may be the case that competing strategic interests will drive a wedge between the quantum resources of competitors and adversaries, partitioning them into a set of smaller networks, divided across strategic boundaries. In this instance, the arguments presented in the upcoming sections will apply to these smaller, isolated networks individually.

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on an exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point tox this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth postulate}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N_t = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

The exact value of the growth rate, $\gamma_N$, is obviously unclear at such early stages and will ultimately be determined empirically. Although in the the case of classical computing we have seen a very consistent doubling of computational power roughly every 18 months. This may very well be different for quantum technologies, owing to their fundamentally different engineering requirements (which are much harder in general).

@@

Let the dollar cost of physical qubits follow Moore's Law-like dynamics, decreasing exponentially with time,
\begin{postulate}[Hardware cost]\label{post:hardware_cost}\index{Hardware cost}
The dollar-cost of a single physical qubit scales inverse exponentially as,
\begin{align}
	C_t = C_0 {\gamma_C}^{-t},
\end{align}
where \mbox{$\gamma_C\geq x1$} characterises the decay rate.
\end{postulate}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment, with \mbox{$Q\to 1$} driven ever closer to unity as market competition increases, thereby closing the gap between investment and reward,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth})\index{Network growth postulate} and employing a combined computational scaling function\index{Combined computational scaling function} (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is the product of the hardware cost per qubit and the number of qubits,
\begin{align}
	n_\text{invest}(t) &= N_t C_t \nonumber \\
	&= N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the time-depenent cost of computation postulate,

\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation, measured in FLOPs per qubit, decreases over time as,
\begin{align}\index{Cost of computation postulate}
	L_t \gtrapprox \frac{C_0 {\gamma_C}^{-t}}{f_\text{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}

This implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation is,
\begin{align}
L_0 \gtrapprox \frac{C_0}{f_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the initial value of computations simply approximates the initial hardware investment, scaled by its initial computational power, as is intuitively expected.

Note that if $f_\text{sc}$ scales linearly, as per classical computation, we observe a regular exponential decay in the cost of computation, consistent with the classical Moore's Law. On the opposing extreme, for exponentially quantum-enhanced $f_\text{sc}$, the cost of computation decreases super-exponentially with time, an economic behaviour unique to post-classical computation with no classical analogue.

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-sharing}, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.

@@

\begin{definition}[Single-qubit QCL]\index{Single-qubit quantum computational leverage}
The single-qubit QCL is the leverage associated with adding a single qubit to the network, \mbox{$n=1$}, defined as,
\begin{align}
	\lambda_\text{qubit} = \frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}.
\end{align}
\end{definition}

@@

Forward contracts are immensely useful in conventional markets, as a means by which to secure future use or ownership of an asset at predictable points in time. For example, farmers make heavy use of forward contracts to lock in sale of their produce before it has been harvested, such that the value is locked in in advance and the sale guaranteed, providing a very valuable hedging instrument\index{Hedging} for managing risk\index{Risk management}.

@@

\comment{Effective ratio of cost increase for isolation vs integration}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{tax_exp} \\
\includegraphics[width=0.47\textwidth]{tax_subsidy}
\caption{(top) Relationship between the tax performance multiplier, (positive) tax rate, and network size, assuming an exponential computational scaling function, in the regime of positive taxation, \mbox{$\gamma_T>1$}. (bottom) For \mbox{$N_\text{tax}=10$}, a zoom into the region around neutral taxation, where \mbox{$\gamma_T\approx 1$}, showing slight degrees of both taxation (\mbox{$\gamma_T>1$}) and subsidisation (\mbox{$\gamma_T<1$}). Neutral taxation, \mbox{$\gamma_T=1$}, is shown in orange.}\label{fig:tax_exp}	
\end{figure}

@@

@@

\subsubsection{The quantum stockmarket}\index{Quantum stockmarket}

As discussed in relation to combined computational scaling functions (Sec.~\ref{sec:comb_comp_sc_func})\index{Combined computational scaling functions}, different market participants will be executing different software applications on their share of the quantum computing resources, with differing QCLs\index{Quantum computational leverage}. Because the applications differ between users, as do their QCLs, so too does the monetary value of the computations they are performing. This yields the distinction between \textit{subjective}\index{Subjective value of computation} and \textit{objective}\index{Objective value of computation} value of computation.

The subjective value of a computation is the value to an end-user of a computation, measured in terms of their associated monetary profit from utilising its output. The objective value, rather, is the cost of the hardware, which is not application specific.

This effetively implies that some users pay more for computation (in terms of RoI\index{Return on investment}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment.

The question then is how to reconcile the distinction between subjective and objective value, given the diversity of applications in the quantum marketplace. This will supercede the na\"ive models for cost of computation presented earlier, which were based entirely on objective value. Of course, subjective value is what people are actually willing to pay for in the real-world!

This will give rise to a marketplace for tradeable units of quantum computation, where the underlying asset is time-shares in the global network. We refer to this as the \textit{quantum stockmarket} -- a marketplace subject to ordinary supply and demand, economic, and psychological pressures. In a scenario where a large number of users are executing computations with high return (think the R\&D lab), asset values will be traded up. Contrarily, in a scenario of low-return computations (think our poor undergrad), they will be traded down. These market forces will be highly time-dependent, varying against many other factors in the economy, such as the emergence of new applications for quantum computing.

The relative market value of computation will subsequently drive the direction of investment into quantum hardware, with carry-over effects on future market prices. If investment stagnates, so too will growth in computational dividends, driving up market rates by limiting supply (assuming positive growth in demand). This will, after market adjustment, drive investment back into the system to satisfy increasing demand. Thus, despite the present uncertainty into the future dynamics of the quantum stockmarket, we expect this positive feedback loop to ensure consistent, ongoing investment into the network, and at least some marginal degree of price stability.

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stockmarket, betting on changes in demand for computation and their associated subjective cost. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their RoI will reflect these market dynamics.

As all markets for tradeable assets do, sophisticated derivative markets will inevitably emerge, whereby people can speculate on or hedge against market dynamics, taking long, short, or more complex market positions, potentially in a highly-leveraged manner. As discussed in Sec.~\ref{sec:for_contr}, derivatives such as future contracts can be extremely helpful in enabling consumers to lock in future prices, creating a stable business climate. Similarly, other derivatives will enable market participants to hedge\index{Hedging} other quantum-related investments. For example, suppose an investor held a stake in an R\&D lab, highly reliant on quantum computing. By taking a leveraged long position on the market value for computation, he may limit losses on his R\&D investment associated with the higher price (and hence lower profit) they will be paying for computation.

No doubt, market manipulation and all the usual nonsense will ensue.
